The `geomnet` package

### 2020-10-11 README.Rmd
- Update to fix changes in dplyr - specifically use `dplyr::n()` - Use `inhereits(dat, "matrix")` instead of `class(x) =! "matrix"` - Adds spell check WORDLIST

You can install `geomnet` directly from CRAN
`install.packages('geomnet')`
or from Github
`devtools::install_github("sctyner/geomnet")`
```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

>>>>

You can install `geomnet` directly from CRAN
`install.packages('geomnet')`
or from Github
`devtools::install_github("sctyner/geomnet")`

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```
